Supplementary Material

### 2024-03-19 article/supplementary.qmd
update article

>>>>

# Relationship between drought indices and land cover change

::: {#fig-varImportance layout-ncol=3}

![Forest](../output/figs/fig_errorbar_resample_random_forest_trends_Forest.png){#fig-varimp_forest}

![Cropland](../output/figs/fig_errorbar_resample_random_forest_trends_Cropland.png){#fig-varimp_crops}

![Grassland](../output/figs/fig_errorbar_resample_random_forest_trends_Grassland.png){#fig-varimp_grass}

![Savanna](../output/figs/fig_errorbar_resample_random_forest_trends_Savanna.png){#fig-varimp_savanna}

![Shrubland](../output/figs/fig_errorbar_resample_random_forest_trends_Shrubland.png){#fig-varimp_shrubs}

![Barren land](../output/figs/fig_errorbar_resample_random_forest_trends_Barren_land.png){#fig-varimp_barren}

Error bar for the variables importance obtained from the 10 resamples folded by the Random Forest.

:::
